Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-26 cogsci2016/paper.tex
results description

\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}

@@

		\begin{figure}[h]
			\centering
			\hspace{-0.73cm}
			\vspace{-0.71cm}
			\includegraphics[width=9.12cm]{./include/tools.pdf}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
			\hspace{-0.42cm}
			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
			\caption{Top: a state of the environment. Middle: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
			\label{env}
		\end{figure}

@@

			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{H1}.

@@

			\begin{figure}[t]
				\center
				\input{include/F.tikz}
				\caption{Flat architecture}
				\label{F}					
			\end{figure}

			\begin{figure}[t]
				\center
				\input{include/H1.tikz}
				\caption{Hierarchy of sensorimotor models}
				\label{H1}					
			\end{figure}

@@

		NN, $100$ iterations of Motor babbling and then $300000$ iterations of the condition. 10 trials per condition, mean and std provided.

@@

			Exploration of the different sensory spaces (number of reached cells in a discretization of the space divided by number of cells).

@@

	\paragraph{}
	We measure the exploration of the different sensory spaces in the $6$ conditions each $5000$ iterations along the $300000$ iterations (Fig. \ref{res_explo}).
	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
	We first show that the Motor Babbling condition (F-RmB) quickly explores $S_{Hand}$ and explores badly $S_{Object}$ and $S_{Boxes}$, compared to the other conditions ($p<0.0001$).
	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
	and explore less $S_{Stick_1}$, $S_{Stick_2}$, $S_{Object}$ and $S_{Boxes}$ than H-RGB-P-AMB condition ($p<0.05$).
	Also, H-RGB-GR-AMB shows lower exploration of $S_{Hand}$, $S_{Stick_2}$ and $S_{Object}$ than H-RGB-P-AMB ($p<0.05$).
	Condition H-RGB-P-AMB-PGITC explores more $S_{Hand}$ ($p<0.01$) and $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB.

	\begin{figure*}[ht]
		\centering
		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}}\\
		\vspace{-0.3cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.pdf}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}

	\paragraph{}
	Fig. \ref{res_interests} shows more details about one (randomly chosen) trial of the condition H1. 
	We can see the interest of each module during the whole experiment.
	The interests of modules 1, 2, 5 are almost stable, as the spaces of interests are high-dimensional and homogeneously reachable: a random exploration will find regions to learn more for more iterations than $300000$.
	The interests of modules 3 and 6 increase abruptly when the object is touch by the corresponding tool.
	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) also corresponding to condition H1.

	\begin{figure*}[ht]
		\centering
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
		\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
		\label{res_interests}
	\end{figure*}

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri, fit}

@@

		\begin{figure}[h]
			\centering
			\hspace{-0.73cm}
			\vspace{-0.59cm}
			\includegraphics[width=9.12cm]{./include/tools.pdf}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
			\hspace{-0.42cm}
			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
			\caption{Top: a state of the environment. Middle: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
			\label{env}
		\end{figure}

@@

			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{Architectures}.

@@

			\begin{figure}[t]
				\center
				\input{include/F.tikz}
				\vspace{-0.25cm}
				\input{include/H1.tikz}
				\vspace{-0.5cm}
				\caption{Architectures. Top: flat. Bottom: hierarchical.}
				\label{Architectures}					
			\end{figure}

@@

		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. 10 trials per condition, mean and std provided.

@@

			We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
			We categorize the behaviors into three types.
			In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus not moved the out-of-reached object.
			The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
			The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.

			Also, for each condition we measure the total exploration of the different sensory spaces during training. 
			The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
			in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
			The exploration of the boxes is the number of boxes that have been filled with the object during training.

@@

	\paragraph{}
	Fig. \ref{res_interests} shows details about one trial of the condition H-RGB-P-AMB. 
	We can see the interest of each module during the whole experiment.
	The interests of modules 2 and 5 increase abruptly once the arm succeeded in grabbing the corresponding stick.
	Following that, the interests of modules 3 and 6 also increase abruptly when the object has been touched by the corresponding stick.
	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) corresponding to the same condition.

	\begin{figure*}[ht]
		\centering
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
		\caption{Condition H-RGB-P-AMB. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
		\label{res_interests}
	\end{figure*}

	\paragraph{}
	Fig. \ref{res_ow} shows the proportion of the three categories of behavior along the $100000$ iterations for conditions H-RGB-GR-AMB and H-RGB-P-AMB.

@@

	\paragraph{}
	Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
	and explore less $S_{Stick_1}$, $S_{Stick_2}$, $S_{Object}$ and $S_{Boxes}$ than H-RGB-P-AMB condition ($p<0.05$).
	Also, H-RGB-GR-AMB shows lower exploration of $S_{Hand}$, $S_{Stick_2}$ and $S_{Object}$ than H-RGB-P-AMB ($p<0.05$).
	Condition H-RGB-P-AMB-PGITC explores more $S_{Hand}$ ($p<0.01$) and $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB.

	\begin{figure*}[ht]
		\centering
		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
		\vspace{-0.3cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.pdf}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}
